---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rrum

[![Build Status](https://travis-ci.org/tmsalab/rrum.svg)](https://travis-ci.org/tmsalab/rrum)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN](http://www.r-pkg.org/badges/version/rrum)](https://cran.r-project.org/package=rrum)
[![Downloads](http://cranlogs.r-pkg.org/badges/rrum?color=brightgreen)](http://www.r-pkg.org/pkg/rrum)

The goal of rrum is to provide an implementation of Gibbs sampling algorithm 
for Bayesian Estimation of **reduced Reparametrized Unifed Model (rRUM)**,
described by Culpepper and Hudson (2017) <doi: 10.1177/0146621617707511>.

## Installation

You can install `rrum` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("rrum")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("tmsalab/rrum")
```

## Usage

To use `rrum`, load the package using:

```{r example}
library("rrum")
```

From here, the rRUM model can be estimated using:

```{r rrum-est, eval = FALSE}
rrum_model = rrum(<data>, <q>)
```

Additional parameters can be accessed with:

```{r rrum-est-adv, eval = FALSE}
rrum_model = rrum(<data>, <q>, chain_length = 10000L,
                  as = 1, bs = 1, ag = 1, bg = 1,
                  delta0 = rep(1, 2^ncol(Q)))
```

`rRUM` item data can be simulated using:

```{r rrum-sim, eval = FALSE}
rrum_items = simcdm::sim_rrum_items(<q>, <rstar>, <pistar>, <alpha>)
```


## Authors

Steven Andrew Culpepper, Aaron Hudson, and James Joseph Balamuta

## Citing the `rrum` package

To ensure future development of the package, please cite `rrum`
package if used during the analysis or simulations. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("rrum")
```

## License

GPL (>= 2)
